Simulation and visualization framework for selecting appropriate urban-scale climate mitigation and adaptation strategies

### 2021-04-14 second_submissions.tex
Revisions

\documentclass[twocolumn, a4paper,10pt]{article}
\usepackage[top=2.5cm, bottom=2.5cm, left=2.0cm, right=2.0cm,
columnsep=0.8cm]{geometry}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{boxedminipage}
\usepackage{nopageno}
\usepackage{graphicx}
\usepackage{natbib}
\usepackage[font=it]{caption}
\usepackage[usenames,dvipsnames]{xcolor}
\usepackage{listings}
\usepackage{caption}
\usepackage{subcaption}
\usepackage{tabularx}
\usepackage{draftwatermark}
\SetWatermarkText{DRAFT}
\SetWatermarkScale{5}
%-----------------------------SET SKIP SPACES -------------------------------------------------------------------
\setlength{\abovecaptionskip}{0pt}
\setlength{\belowcaptionskip}{3pt}
\setlength{\parindent}{0pt}
\setlength{\parskip}{3pt}
%\renewcommand{\baselinestretch}{0.7}
% FOR enumerates
\setlist{itemsep=-0.1cm,topsep=0.1cm,labelsep=0.3cm}
\setenumerate{leftmargin=*}
\setcounter{secnumdepth}{-1}
%-----------------------------SET FONTS -------------------------------------------------------------------
% Set fonts for title, section and subsection headings
\makeatletter
\renewcommand\title[1]{\gdef\@title{\fontsize{12pt}{2pt}\bfseries{#1}}}
\makeatletter
\renewcommand\section{\@startsection{section}{1}{\z@}{3pt}{3pt}{\normalfont\large\bfseries}}
% \normalfont\large
\makeatletter
\renewcommand\subsection{\@startsection{subsection}{1}{\z@}{\z@}{\z@}{\normalfont\normalsize\bfseries}}
\makeatletter
\renewcommand\subsection{\@startsection{subsection}{1}{\z@}{\z@}{0.1pt}{\normalfont\normalsize\bfseries}}
\renewcommand\refname{References}
%END OF THE SETUP
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Simulation and visualisation of mitigation and adaption strategy pathways for urban districts
%%%%%%%%%%%%%%%%%%%%%%%%   TITLE   %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%% Please keep the \vspace{4pt} at the top
\title{%
Simulation and visualization framework for selecting appropriate urban-scale climate mitigation and adaptation strategies} 																																% Line 2 
%If there is no second line then just put \phantom{Line 2} here
%%% Change or delete text before "\\" on the lines below to keep the layout but don't remove the "\\"
%%% Do not exceed more than 6 lines for authors and affiliations
\author{																																														% Line 3
Justin McCarty$^1$, Adam Rysanek$^1$
\\ 																				% Line 4
% $^1$The University of British Columbia, Vancouver, Canada
\\ 																																                                                            	% Line 5
% $^2$Institution 2, City 2, Country 2
\\ 																																                                                                % Line 6
% comment the lines below and add \phantom{} lines as needed to reach a total of 10 lines
% \textit{(The names and affiliations SHOULD NOT be included in the draft submitted for review)}
\\ 			 			  	                                                    % Line 7
% \textit{(leave blank up to line 10 - remove line numbering from final version)}
\\ 														                    	% Line 8
\phantom{Line 9}} 																																								            	% Line 9
\date{\vspace{-0.5cm}}	% remove default date and replace the Blank 10th line														                                                            % Line 10
%END OF THE TITLE
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{document}

@@

\begin{figure*}[hbpt]
    \centering
    \includegraphics[scale=0.50]{figures/wesbrook_plan.eps}
    \caption{The baseline UBEM for Wesbrook Village in BC.}
    \label{fig:wesbrook_base}
\end{figure*}

@@

% \begin{figure}
%     \centering
%     \includegraphics[scale=1.5]{figures/sample_sequence.eps}
%     \caption{Each scenario iterated through 256 combinations of strategy implementation.}
%     \label{fig:sample_sequence}
% \end{figure}

\subsection*{Wesbrook Village} 
% Simulation will be exhaustive of the different combinations in the pool of strategies and scenarios allowing each strategy to be measured independently as well as determine combinations that are more or less efficient than individual implementation under the entire range of uncertainty.
Wesbrook Village is a new residential community under construction by the University of British Columbia (UBC) \citep{ubc_planning_ubc_2020_SR, ubc_planning_ubc_2020_wb}. On it completion within the next decade, the community will provide permanent housing for over 25,000 residents of Vancouver, BC primarily in mid-rise (4-6 stories) and high-rise residential towers (15-30 stories).

@@

 Buildings of the Wesbrook community make use of mix of energy systems. Some buildings provide space heating using hydronic in-floor radiant systems; some provide space heating via electric baseboard heaters. Some buildings operate dedicated boilers for generating hot water; other buildings receive hot water from a natural gas-fired district energy system.  This district heating system is described in the context of a UBEM in \citet{mccarty_accepted_2020}. Centralized space cooling has not been provided for across the development, but concerns around the potential need for future space cooling is a growing concern for naturally-ventilated buildings in the region \citep{rysanek_forecasting_2021}. With its current building codes, UBC does intend that space cooling may be a required energy service in the community in the next decade \citep{noauthor_residential_2021}.

\begin{table*}[ht]
    \vspace{-5pt}   % Please use appropriate negative vspace to remove the space above/belovw the Table
    \caption{Each strategy as it was applied in the simulations.}
    \footnotesize
    \label{tab:strategies}
    \centering
    % \begin{tabularx}{\textwidth}{|X|X|X|}
    \begin{tabularx}{\linewidth}{|>{\hsize=0.2\hsize}X|
                              >{\hsize=0.5\hsize}X|
                              >{\hsize=0.3\hsize}X|}
        \hline
        \bf{Strategy} & \bf{Description} & \bf{Scale} \\
        \hline
        Adjust Comfort Threshold & Raise cooling setpoints 1C and reduce heating setpoints 1C & All Buildings \\
        \hline
        Green Roof & Install green roofs for insulative, albedo, and heat gain benefits. & All Buildings \\
        \hline
        Deep Envelope and HVAC Retrofit & Install heat pumps for space heating and DHW along with high performance shells and reduced window-wall ratios & Existing Buildings \\
        \hline
        Passive House & Require passive house building codes for envelope. & New Buildings \\
        \hline
        Heat Pumps & Install heat pumps for space heating, cooling and DHW. & All buildings \\
        \hline
        Mass Timber & Construction must utilize mass timber. & New Buildings \\
        \hline
        Seawater Cooling Loop & Buildings get space cooling from heat pump that is amplified with a seawater cooling loop & All Buildings \\
        \hline
        Rooftop Photovoltaic & Install grid-tied rooftop solar with net-metering & All Buildings \\
        \hline
    \end{tabularx}
    \vspace{-5pt}   % Please use appropriate negative vspace to remove the space above/belovw the Table
\end{table*}

@@

% \begin{table*}[h]
%     \vspace{-5pt}   % Please use appropriate negative vspace to remove the space above/belovw the Table
%     \caption{The first two-column table.}
%     \label{tab:code_trajectory}
%     \centering
%     \begin{tabular}{ | c | c | c | }
%         \hline
%         \bf{Year} & \bf{Code Name} 2 & \bf{Performance Note} \\
%         \hline
%         2005 & REAP2.1 & Wall U-Value = 0.4 W/m²K \\
%         \hline
%         2005 & REAP2.1 & Wall U-Value = 0.4 W/m²K \\
%         \hline
%         2005 & REAP2.1 & Wall U-Value = 0.4 W/m²K \\
%         \hline
%         2005 & REAP2.1 & Wall U-Value = 0.4 W/m²K \\
%         \hline
%     \end{tabular}
%     \vspace{-5pt}   % Please use appropriate negative vspace to remove the space above/belovw the Table
% \end{table*}

@@

The EnergyPlus Weather (EPW) file for Vancouver, BC produced by \citet{cwec_2016} was morphed, following the algorithms set out by \citet{belcher_constructing_2005} and expanded upon by \citet{jentsch_climate_2008}. Two climate pathways are followed, discussed in this paper as the \textit{best-case} and \textit{worst-case} scenarios. These are \textit{Shared Socioeconomic Pathway 1} (SSP126) and \textit{Shared Socioeconomic Pathway 5} (SSP585)
defined in \citet{oneill_roads_2017}. Two morphed climate files were produced at 2050 and 2080 for each pathway.

% and described in Figure \ref{fig:weatherfiles}.

@@

A single entire simulation process (1024 iterations) required 64 hours of processing, utilizing 14 threads from an Intel i9-9900 8-core CPU at 4.6GHz, requiring 20GB of free RAM and an end storage requirement over 2TB of uncompressed results files. This detail is mentioned to help readers understand the scale of computing required to undertake simulations of this scale and to seek methods and functions that optimize processing times.

\subsection*{Total Annualized Cost}
Components and technology costs was gathered through several data sources, \citep{noauthor_cpcn_2014,schlueter_3for2_2016,salasovich_energy_2016,kegel_life_nodate,gordian_rsmeans_2020}. Cost is a highly uncertain data point to incorporate into building energy models. Cost is assessed as the net difference between a strategy-set and the baseline, each calculated as the 30-year total annualized cost (TAC) from within the City Energy Analyst, applying a 5\% discount rate.

\begin{figure}[t!]
    \centering
    \captionsetup{margin=.5cm}
    \includegraphics[scale=0.8]{figures/general_results_box.eps}
    \caption{General results from the iterations presented across total emissions over 30 years and net 30-year total annualized cost.}
    \label{fig:cross_plot}
\end{figure}

\begin{figure}[t!]
    \centering
    \includegraphics[scale=1.15]{figures/district_heat_charts.eps}
    \caption{Comparing the demand on the partially natural gas fed district heat system across the baseline scenarios in the end of century best- (SSP126) and worst-case (SSP585) scenarios. The highlighted gap between the two curves shows where less natural gas was used in the SSP585 scenario.}
    \label{fig:compare_district}
\end{figure}

@@

\subsection*{Operational and embodied carbon}
Operational carbon is taken as the carbon emitted over a 30 year period from each building as a result of energy consumption for plug-load, heating and cooling, and ventilation service. BC's electrical grid is served by a hydroelectric power provider and is a low-carbon source, at 10.8 kgCO2e/kWh \citep{bc_ministry_of_envrionmetn_and_climate_change_strategy_bc_2019}. The district heating provider intends for the system tobe  fed entirely from natural gas boilers until 2023 at which point the transition to a more complex system of natural gas peaking boilers and electric heat pumps. This system was previously modelled in \citet{mccarty_accepted_2020}. Its carbon intensity was estimated to be between an annual average of 10.8 and 180.0 kgCO2e/kWh. The range is due to fluctuations in the amount of natural gas used in the system, as well as the amount of waste heat available to create a more efficient lift in the heat pumps. Limits imposed on heat pump and waste heat capacity are drawn from the operator in \citet{noauthor_infrastructure_2014}.

The embodied carbon of components and technologies of the models was gathered, similar to the cost data, from a variety of sources \citep{jones_ice_2019, droguett_embodied_2019,c-change_labs_embodied_2020}, and are cradle-to-gate accounts of embodied carbon. The limitation with disparate data sources in this portion of the research generally has to do with the geography of the components involved. An effort was made to first gather data from sources specific the BC or the Pacific Northwest region of the US and than from North America as a whole, before seeking data from further away.

%---------------------------------------------------------------------------------------
\section*{Results}

The simulation procedure was executed for 1024 scenarios, producing hourly demand results for each building within the simulation space, as well as annual cost and emissions results for each building. For iterations in which rooftop-photovoltaic was an option a set of results was generated to be used in correcting total grid-demand for the electricity generated by the rooftop-photovoltaic. From these iterations several MACCs were constructed in Figures \ref{fig:MACC_budget}, \ref{fig:MACC_threshold}, and \ref{fig:true_macc_both}. The first two are \textit{illustrative} MACCs in that they present a set of possible interventions, but not necessarily a pathway through which those interventions can be connected. The latter two are \textit{true} MACCs as described in Figure \ref{fig:true_macc_both}.

@@

\begin{figure}[hbpt]
    \centering
    \captionsetup{margin=.5cm}
    \includegraphics[scale=0.95]{figures/true_maccs_waterfalls_both.eps}
    \caption{Plotting marginal abatement cost and the adaptation metric to serve as a canvas for pathway planning.}
    \label{fig:true_macc_both}
\end{figure}

\begin{figure}[t!]
    \centering
    \captionsetup{margin=.5cm}
    \includegraphics[scale=0.45]{figures/pareto_plots_585_box_update.eps}
    \caption{Plotting marginal abatement cost and the adaptation metric to serve as a canvas for pathway planning.}
    \label{fig:pareto_plot}
\end{figure}

Of the two \textit{true} MACCs used in this study, the first represents a strategy-set that was chosen based on a high degree of adaptability present, while also abating a large amount of emissions. This was done under the worst-case climate scenario and the selected strategy-set is \textit{00011111}, highlighted in Figure \ref{fig:pareto_plot}. Marginal abatement cost and the adaptation metric were plotted in Figure \ref{fig:pareto_plot} to evaluate optimal fronts of each scenario.

@@

% \begin{figure}[t]
%     \centering
%     \includegraphics[scale=0.8]{figures/true_macc_noDH_waterfall_comb.eps}
%     \caption{Plotting marginal abatement cost and the adaptation metric to serve as a canvas for pathway planning.}
%     \label{fig:MACC_true_noDH}
% \end{figure}

A second \textit{true} MACC was generated under the plan to abate as many emissions as possible while continuing to use the district heating system, under the worst-case climate scenario. Figure \ref{fig:true_macc_both} describes how each measure contributes to overall emissions reduction. The resulting MACC shows a more consistent scale of MAC and overall abatement between measures that the previous example, but total abatement is only 8\% of the baseline's emissions.

% \begin{figure}[t]
%     \centering
%     \includegraphics[scale=0.8]{figures/true_macc_DH_waterfall_comb.eps}
%     \caption{Plotting marginal abatement cost and the adaptation metric to serve as a canvas for pathway planning.}
%     \label{fig:MACC_true_DH}
% \end{figure}

% \begin{figure*}[hbpt]
%     \centering
%     \includegraphics[scale=0.8]{figures/optimal_plots.eps}
%     \caption{Plotting marginal abatement cost and the adaptation metric to serve as a canvas for pathway planning.}
%     \label{fig:pareto_plot}
% \end{figure*}

%---------------------------------------------------------------------------------------
\section*{Discussion}

\subsection*{Abatement after fuel-switching}
The context for this study sets up an interesting proposition within BC. Electricity in BC is provided primarily via hydroelectricity. Emissions within the building sector are therefore driven by natural gas use, either on-site or within district systems. The two \textit{true} MACC cases show that in order to reach large reductions over the baseline condition, the use of natural gas must be eliminated. This however raises the point of how abatement should continue once the significant reductions are made and systems are then relying on a near-carbon-free grid. At present, BC (and UBC) expects new buildings to be net-zero \textit{energy} ready by the early 2030s, with no clear objectives on whether buildings should be truly net-zero energy (NZE) in a more distant future. There is reason for this, as evidenced by the modelling undertaken in this work. This study showed that in testing rooftop PV systems for medium density developments, PV systems will not yield large emissions reductions under any scenario. In the worst-case climate scenario rooftop panels alone reduced emissions by only 4.4\%.

%Additionally building-based sequestration methods offer a potential avenue for meeting net-zero \textit{carbon} goals \citep{skullestad_high-rise_2016}. This study did not consider the Mass Timber strategy to be carbon sequestering, but it is less intensive than cement-based building, leading to between 60 and 300 Tonnes of carbon abated, depending on the development scenario.

@@

%---------------------------------------------------------------------------------------
\section*{Conclusion}
In this study the output of 1024 different urban building energy simulations was used to generate marginal abatement cost curves and complimentary visualizations to make decisions on climate mitigation and adaptation at an urban scale. A case study of Wesbrook Village, a planend 25,000-member residential community in Vancouver, Canada was used.

@@

% using a plot of pareto optimums (Figure \ref{fig:pareto_plot}). This enables planners to begin to assess adaptation targets alongside abatement.

The analysis had limitations discussed in the literature on using MACCs for decision-support. These include being more realistic about building technology and component lifetimes, which requires the framework to consider retirement. As well the study is constrained by computational resources and known mitigation and adaptation strategies for the site. Future studies should seek to better understand either through exploratory analysis or expert elicitation, which strategies are reasonable for the market and context. This will also aide in developing a cost and carbon database.

@@

%---------------------------------------------------------------------------------------
\section*{Acknowledgment}

>>>>

\documentclass[twocolumn, a4paper,10pt]{article}
\usepackage[top=2.5cm, bottom=2.5cm, left=2.0cm, right=2.0cm,
columnsep=0.8cm]{geometry}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{boxedminipage}
\usepackage{nopageno}
\usepackage{graphicx}
\usepackage{natbib}
\usepackage[font=it]{caption}
\usepackage[usenames,dvipsnames]{xcolor}
\usepackage{listings}
\usepackage{caption}
\usepackage{subcaption}
\usepackage{tabularx}
%-----------------------------SET SKIP SPACES -------------------------------------------------------------------
\setlength{\abovecaptionskip}{0pt}
\setlength{\belowcaptionskip}{3pt}
\setlength{\parindent}{0pt}
\setlength{\parskip}{3pt}
%\renewcommand{\baselinestretch}{0.7}
% FOR enumerates
\setlist{itemsep=-0.1cm,topsep=0.1cm,labelsep=0.3cm}
\setenumerate{leftmargin=*}
\setcounter{secnumdepth}{-1}
%-----------------------------SET FONTS -------------------------------------------------------------------
% Set fonts for title, section and subsection headings
\makeatletter
\renewcommand\title[1]{\gdef\@title{\fontsize{12pt}{2pt}\bfseries{#1}}}
\makeatletter
\renewcommand\section{\@startsection{section}{1}{\z@}{3pt}{3pt}{\normalfont\large\bfseries}}
% \normalfont\large
\makeatletter
\renewcommand\subsection{\@startsection{subsection}{1}{\z@}{\z@}{\z@}{\normalfont\normalsize\bfseries}}
\makeatletter
\renewcommand\subsection{\@startsection{subsection}{1}{\z@}{\z@}{0.1pt}{\normalfont\normalsize\bfseries}}
\renewcommand\refname{References}
%END OF THE SETUP
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Simulation and visualisation of mitigation and adaption strategy pathways for urban districts
%%%%%%%%%%%%%%%%%%%%%%%%   TITLE   %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%% Please keep the \vspace{4pt} at the top
\title{%
Simulation and visualization framework for selecting appropriate urban-scale climate mitigation and adaptation strategies} 																																% Line 2 
%If there is no second line then just put \phantom{Line 2} here
%%% Change or delete text before "\\" on the lines below to keep the layout but don't remove the "\\"
%%% Do not exceed more than 6 lines for authors and affiliations
\author{																																														% Line 3
% Justin McCarty$^1$, Adam Rysanek$^1$
\\ 																				% Line 4
% $^1$The University of British Columbia, Vancouver, Canada
\\ 																																                                                            	% Line 5
% $^2$Institution 2, City 2, Country 2
\\ 																																                                                                % Line 6
% comment the lines below and add \phantom{} lines as needed to reach a total of 10 lines
% \textit{(The names and affiliations SHOULD NOT be included in the draft submitted for review)}
\\ 			 			  	                                                    % Line 7
% \textit{(leave blank up to line 10 - remove line numbering from final version)}
\\ 														                    	% Line 8
\phantom{Line 9}} 																																								            	% Line 9
\date{\vspace{-0.5cm}}	% remove default date and replace the Blank 10th line														                                                            % Line 10
%END OF THE TITLE
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{document}

@@

\begin{figure}[hbpt]
    \centering
    \includegraphics[scale=0.28]{figures/wesbrook_plan.eps}
    \caption{The baseline UBEM for Wesbrook Village in BC.}
    \label{fig:wesbrook_base}
\end{figure}

@@

\subsection*{Wesbrook Village}

Wesbrook Village is a new residential community under construction by the University of British Columbia (UBC) \citep{ubc_planning_ubc_2020_SR, ubc_planning_ubc_2020_wb}. On its completion within the next decade, the community will provide permanent housing for over 25,000 residents of Vancouver, BC primarily in mid-rise (4-6 stories) and high-rise residential towers (15-30 stories).

@@

Buildings of the Wesbrook community make use of mix of energy systems. Some buildings provide space heating through hydronic in-floor radiant systems; some through electric baseboard heaters. Some buildings operate dedicated boilers for generating hot water; other buildings receive hot water from a natural gas-fired district energy system. This district heating system is described in the context of a UBEM in \citet{mccarty_accepted_2020}. Centralized space cooling has not been provided for across the development, but concerns around the potential need for future space cooling is a growing concern for naturally-ventilated buildings in the region \citep{rysanek_forecasting_2021}. With its current building codes, UBC does intend that space cooling may be a required energy service in the community in the next decade \citep{noauthor_residential_2021}.

\begin{table*}[ht]
    \vspace{-5pt}   % Please use appropriate negative vspace to remove the space above/belovw the Table
    \caption{Each strategy as it was applied in the simulations.}
    \footnotesize
    \label{tab:strategies}
    \centering
    % \begin{tabularx}{\textwidth}{|X|X|X|}
    \begin{tabularx}{\linewidth}{|>{\hsize=0.2\hsize}X|
                              >{\hsize=0.4\hsize}X|
                              >{\hsize=0.15\hsize}X|
                              >{\hsize=0.25\hsize}X|}
        \hline
        \bf{Strategy} & \bf{Description} & \bf{Scale} & \bf{Embodied CO\textsubscript{e} Source} \\
        \hline
        Adjust Comfort Threshold & Raise cooling setpoints 1C and reduce heating setpoints 1C & All Buildings & N/A \\
        \hline
        Green Roof & Install green roofs for insulation, albedo, and heat gain benefits. & All Buildings & \citep{jones_ice_2019}\\
        \hline
        Deep Envelope and HVAC Retrofit & Install heat pumps for space heating and DHW along with high performance shells and reduced window-wall ratios & Existing Buildings & \citep{jones_ice_2019, rodriguez_embodied_2019} \\
        \hline
        Passive House & Require passive house building codes for envelope. & New Buildings & \citep{jones_ice_2019} \\
        \hline
        Heat Pumps & Install heat pumps for space heating, cooling and DHW. & All buildings & \citep{rodriguez_embodied_2019} \\
        \hline
        Mass Timber & Construction must utilize mass timber. & New Buildings & \citep{c-change_labs_embodied_2020} \\
        \hline
        Seawater Cooling Loop & Buildings get space cooling from heat pump that is amplified with a seawater cooling loop & All Buildings & \citep{noauthor_cpcn_2014, jones_ice_2019} \\
        \hline
        Rooftop Photovoltaic & Install grid-tied rooftop solar with net-metering & All Buildings  & \citep{jones_ice_2019} \\
        \hline
    \end{tabularx}
    \vspace{-5pt}   % Please use appropriate negative vspace to remove the space above/belovw the Table
\end{table*}

@@

@@

The EnergyPlus Weather (EPW) file for Vancouver, BC produced by \citet{cwec_2016} was morphed, following the algorithms set out by \citet{belcher_constructing_2005} and expanded upon by \citet{jentsch_climate_2008}. A 25-member ensemble of climate model output data from Climate Model Intercomparison Project 6 (CMIP6) models was used in the morphing process. Two climate pathways are followed, discussed in this paper as the \textit{best-case} and \textit{worst-case} scenarios. These are \textit{Shared Socioeconomic Pathway 1} (SSP126) and \textit{Shared Socioeconomic Pathway 5} (SSP585)
defined in \citet{oneill_roads_2017}. Two morphed climate files were produced at 2050 and 2080 for each pathway.

@@

% A single entire simulation process (1024 iterations) required 64 hours of processing, utilizing 14 threads from an Intel i9-9900 8-core CPU at 4.6GHz, requiring 20GB of free RAM and an end storage requirement over 2TB of uncompressed results files. This detail is mentioned to help readers understand the scale of computing required to undertake simulations of this scale and to seek methods and functions that optimize processing times.

\subsection*{Total Annualized Cost}
Components and technology costs was gathered through several data sources, \citep{noauthor_cpcn_2014,schlueter_3for2_2016,salasovich_energy_2016,kegel_life_nodate,gordian_rsmeans_2020}. Cost is a highly uncertain data point to incorporate into building energy models. Cost is assessed as the net difference between a strategy-set and the baseline, each calculated as the 30-year total annualized cost (TAC), shown in Eq. 1, from within the City Energy Analyst, applying a 5\% discount rate, which was chosen after consulting the local developers and planners.

\begin{equation}
C_{ann,tot} = CRF(i,R)C_{NPC,tot}
\end{equation}

Total Annualized Cost is the annualized value of the total net present cost where \textit{CRF} is the Cost Recovery Factor, requiring \textit{i}, the annual real discount rate, and \textit{R}, the lifetime considered. C\textsubscript{NPC,tot} is the total net present cost for the lifetime considered.

\begin{figure}[t]
    \centering
    \captionsetup{margin=.5cm}
    \includegraphics[scale=0.8]{figures/general_results_box.eps}
    \caption{General results from the iterations presented across total emissions over 30 years and net 30-year total annualized cost.}
    \label{fig:cross_plot}
\end{figure}

\begin{figure}[t]
    \centering
    \includegraphics[scale=1.15]{figures/district_heat_charts.eps}
    \caption{Here we compare the demand on the district heating system and show, in the highlighted gap, where less natural gas was used due to the generally warmer winter in SSP585.}
    \label{fig:compare_district}
\end{figure}

@@

\subsection*{Operational and embodied carbon}
Operational carbon is taken as the carbon emitted over a 30 year period from each building as a result of energy consumption for plug-load, heating and cooling, and ventilation service. BC's electrical grid is served by a hydroelectric power provider and is a low-carbon source, at 10.8 kgCO2e/kWh \citep{bc_ministry_of_envrionmetn_and_climate_change_strategy_bc_2019}. The district heating provider intends for the system to be fed entirely from natural gas boilers until 2023 at which point there will be a transition to a more complex system of natural gas peaking boilers and wate-heat primed electric heat pumps. This system was previously modelled in \citet{mccarty_accepted_2020}. Its carbon intensity was estimated to be between an annual average of 10.8 and 180.0 kgCO2e/kWh. The range is due to fluctuations in the amount of natural gas used in the system, as well as the amount of waste heat available to create a more efficient lift in the heat pumps. Limits imposed on heat pump and waste heat capacity are drawn from the operator in \citet{noauthor_infrastructure_2014}.

The embodied carbon of components and technologies of the models was gathered, similar to the cost data, from a variety of sources \citep{jones_ice_2019, droguett_embodied_2019,c-change_labs_embodied_2020}, and are cradle-to-gate. The limitation with disparate data sources in this portion of the research generally has to do with the geography of the components involved. An effort was made to first gather data from sources specific the BC or the Pacific Northwest region of the US and than from North America as a whole, before seeking data from further away.

%---------------------------------------------------------------------------------------
\section*{Results}
The simulation procedure was executed for 1024 scenarios, producing hourly demand results for each building within the simulation space, as well as annual cost and emissions results for each building. For iterations in which rooftop-photovoltaic was an option a set of results was generated to be used in correcting total grid-demand for the electricity generated by the rooftop-photovoltaic. From these iterations several MACCs were constructed in Figures \ref{fig:MACC_budget}, \ref{fig:MACC_threshold}, and \ref{fig:true_macc_both}. The first two are \textit{illustrative} MACCs in that they present a set of possible interventions, but not necessarily a pathway through which those interventions can be connected. The latter two are \textit{true} MACCs as described in \ref{fig:true_macc_both}.

@@

\begin{figure}[hbpt]
    \centering
    \captionsetup{margin=.5cm}
    \includegraphics[scale=0.95]{figures/true_maccs_waterfalls_both.eps}
    \caption{Here two sets of plots are shown for two strategy sets. The top of each set shows the contribution of each strategy to the the strategy set's overall carbon emissions reduction. The bottom shows the MAC breakdown within each strategy set.}
    \label{fig:true_macc_both}
\end{figure}

Of the two \textit{true} MACCs used in this study, the first represents a strategy-set that was chosen based on a high degree of adaptability present, while also abating a large amount of emissions. This was done under the worst-case climate scenario and the selected strategy-set is \textit{00011111} is highlighted in Figure \ref{fig:pareto_plot}. Marginal abatement cost and the adaptation metric were plotted in Figure \ref{fig:pareto_plot} to evaluate optimal fronts of each scenario.

@@

A second \textit{true} MACC was generated under the plan to abate as much carbon as possible while continuing to use the district heating system, under the worst-case climate scenario. Figure \ref{fig:true_macc_both} describes how each measure contributes to overall emissions reduction. The resulting MACC shows a more consistent scale of MAC and overall abatement between measures that the previous example, but total abatement is only 8\% of the baseline's emissions.

\begin{figure}[t!]
    \centering
    \captionsetup{margin=.5cm}
    \includegraphics[scale=0.40]{figures/pareto_plots_585_box_update.eps}
    \caption{Plotting marginal abatement cost and the adaptation metric to serve as a canvas for pathway planning.}
    \label{fig:pareto_plot}
\end{figure}
%---------------------------------------------------------------------------------------
\section*{Discussion}

\subsection*{Abatement after fuel-switching}
The context for this study sets up an interesting proposition within BC. Electricity in BC is provided primarily via hydroelectricity; the electrical gird is considered 98\% clean energy \citep{bc_ministry_of_envrionmetn_and_climate_change_strategy_bc_2019}. Emissions within the building sector are therefore driven by natural gas use, either on-site or within district systems. The two \textit{true} MACC cases show that in order to reach large reductions over the baseline condition, the use of natural gas must be eliminated. This however raises the point of how abatement should continue once the significant reductions are made and systems are then relying on a near-carbon-free grid. At present, BC (and UBC) expects new buildings to be net-zero \textit{energy} ready by the early 2030s, with no clear objectives on whether buildings should be truly net-zero energy (NZE) in a more distant future. There is reason for this, as evidenced by the modelling undertaken in this work. This study showed that in testing rooftop PV systems for medium density developments, PV systems will not yield large emissions reductions under any scenario. In the worst-case climate scenario rooftop panels alone reduced emissions by only 4.4\%.

Additionally building-based sequestration methods offer a potential avenue for meeting net-zero \textit{carbon} goals \citep{skullestad_high-rise_2016}. This study did not consider the Mass Timber strategy to be carbon sequestering, but it is less intensive than cement-based building, leading to between 60 and 300 Tonnes of carbon abated, depending on the development scenario. An increase in emissions is seen with the implementation of a seawater cooling loop, likely due to the fact that conventional methods of space cooling rely on a near-zero carbon grid to begin with and are not as intense from an embodied carbon perspective.

@@

In creating the morphed weather files, we used climate model data from global climate models and not regional climate models. This is typical practice for morphing, particularly if you want to adjust weather variables beyond temperature. However it is a limitation particularly in a region such as Southwestern, BC that is highly mountainous and coastal. Future efforts for morphing should address these limitations with climate model data that is either regionally generated or downscaled.

The increase in cost of energy services was not accounted for dynamically. It would be expected, particularly in a country with a progressive carbon tax, that the cost of natural gas and electricity will increase over the coming decades, and outpace inflation-related increases. Future analysis must take this into account, as well as seek to differ the increase across climate change scenarios, which have different economic assumptions underpinning their respective increases in greenhouse gas emissions.
%---------------------------------------------------------------------------------------
\section*{Conclusion}
In this study the output of 1024 different urban building energy simulations was used to generate marginal abatement cost curves and complimentary visualizations to make decisions on climate mitigation and adaptation at an urban scale. A case study of Wesbrook Village, a planned 25,000-member residential community in Vancouver, Canada was used.

@@

The analysis had limitations discussed in the literature on using MACCs for decision-support. These include being more realistic about building technology and component lifetimes, which requires the framework to consider retirement. As well the study is constrained by computational resources (each 1024 iteration took 64 hours) and known mitigation and adaptation strategies for the site. Future studies should seek to better understand either through exploratory analysis or expert elicitation, which strategies are reasonable for the market and context. This will also aide in developing a cost and carbon database.

@@

%---------------------------------------------------------------------------------------
\section*{Acknowledgment}
This project was funded by the Pacific Institute for Climate Solutions (PICS) Energy Efficiency in the Built Environment Project (grant number PICS 36170-50280).
